---
title: "Custom input and output files"
output: html_notebook
---

# Do first

1. Navigate to the `5-files/` folder.
2. Open `5-files.Rproj` as an RStudio project in a new R session. (Click on `5-files.Rproj` in RStudio's file manager.)
3. Check that your working directory is correct. It should be `5-files/`.

```{r}
basename(getwd()) # Should be "5-files"
```

4. Run the setup chunk below.

```{r, include = FALSE}
source("../config/options.R")
```

# Reproducible file management

Some targets depend on external files. When you edit a file, you want `make()` to run all the affected targets. To tell `drake` to pay attention to files, there are special functions to identify files in your plan. 

Function | Purpose | Works with directories? | Works inside custom functions?
---|---|---|---
`file_in()` | Track **input** files. | Yes | Yes
`file_out()` | Track **output** files | Yes | No
`knitr_in()` | Track `knitr` report files | No | No

For now, let's focus on `file_in()` and` file_out()`. We have already seen `file_in()` in our previous plans.

```{r, message = FALSE}
source("R/packages.R")
source("R/functions.R")
source("R/plan.R")
plan %>%
  filter(target == "data") %>%
  pull(command) %>%
  `[[`(1)
```

`file_in()` tells `make()` to fingerprint and track `customer_churn.csv`. As we saw in the `3-flow` exercises, `drake` updates the downstream targets when the data file changes.

```{r}
config <- drake_config(plan)
vis_drake_graph(config, from = file_store("../data/customer_churn.csv"))
```

`file_out()` works similarly, but for output files. Output files from upstream targets can serve as input files to downstream targets.

```{r}
example_plan <- drake_plan(
  data_file_target = {
    data1 <- read_csv(file_in("input.csv"))
    data2 <- munge(data)
    write_csv(data1, file_out("data1.csv"))
    write_csv(data2, file_out("data2.csv"))
  },
  analysis_target = analyze_files(file_in(c("data1.csv", "data2.csv")))
)

config <- drake_config(example_plan)
vis_drake_graph(config)
```

# Exercise: back to customer churn

Instead of letting `drake` save our model automatically, let's manually save it to a custom file. That way, the return value of the target can be something else: say, the progression of the model fit over each epoch (<https://keras.rstudio.com/reference/fit.html#value>). To manually save the model, we use the [`save_model_hdf5()`](https://keras.rstudio.com/reference/save_model_hdf5.html) and `load_model_hdf5()` from `keras`. (This is what `drake` uses when you insert `format = "keras"` in the plan.)

Your turn: follow the directions in the comments of `R/plan.R` and `R/functions.R` to save the model to a reproducibly-tracked HDF5 file. If you get stuck and need to reset your files, start over with a fresh copy of the notebooks and supporting files ([`learndrake::save_notebooks()`](https://github.com/wlandau/learndrake)). You can peek at [this chapter of the manual](https://ropenscilabs.github.io/drake-manual/churn.html#increasing-efficiency) for hints.

When you are done, check your dependency graph.

```{r}
source("R/packages.R")
source("R/functions.R")
source("R/plan.R")
config <- drake_config(plan)
vis_drake_graph(config, hover = TRUE)
```

Your graph should look something like this.

```{r}
readRDS("img/graph.rds")
```

Now let's run the workflow.

```{r}
make(plan)
```

Sanity check: are all the targets up to date now?

```{r}
outdated(config)
```

```{r}
make(plan)
```

As promised, file-based approach frees us up to see the progression of the model run.

```{r}
loadd(progression)
plot(progression)
```

The model is in the file.

```{r}
load_model_hdf5("model.h5")
```

What happens if we remove it?

```{r}
unlink("model.h5")
```

Which targets are outdated now?

```{r}
outdated(config)
```

Which targets get rebuilt when you call `make(plan)`?

```{r}
make(plan)
```
