---
output: github_document
---

[![Launch RStudio Cloud](https://img.shields.io/badge/RStudio-Cloud-blue)](https://rstudio.cloud/project/627076)
[![Launch RStudio Binder](http://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/wlandau/learndrake/binder?urlpath=rstudio)
[![Travis build status](https://travis-ci.org/wlandau/learndrake.svg?branch=master)](https://travis-ci.org/wlandau/learndrake)
[![Codecov test coverage](https://codecov.io/gh/wlandau/learndrake/branch/master/graph/badge.svg)](https://codecov.io/gh/wlandau/learndrake?branch=master)

# The drake short course

`learndrake` is a free online short course on the [`drake` R package](https://github.com/ropensci/drake). With guided web-based hands-on exercises, you will gradually build up a [`drake`](https://github.com/ropensci/drake)-powered [machine learning project](https://blogs.rstudio.com/tensorflow/posts/2018-01-11-keras-customer-churn/) and practice the fundamentals of  [`drake`](https://github.com/ropensci/drake). If you run into trouble or have questions along the way, please post an issue at <https://github.com/wlandau/learndrake> to ask for help.

## How to take the course

1. Read the intro slides at <https://wlandau.github.io/learndrake> and watch the video recording at <https://ropensci.org/commcalls/2019-09-24>.
2. Sign up for a free RStudio Cloud account at <https://rstudio.cloud>.
3. Log into the public RStudio Cloud workspace at <https://rstudio.cloud/project/627076>. You are now running an instance of RStudio Server with everything you need.
4. In the "Files" pane of the IDE, locate the numbered folders with `*.Rmd` notebooks inside. Work through the notebooks in order.

Topic | Notebook
---|---
Custom functions | `1-functions/1-functions.Rmd`
`drake` plans | `2-plans/2-plans.Rmd`
Changing workflows | `3-changes/3-changes.Rmd`
Static branching | `4-static/4-static.Rmd`
Dynamic branching | `5-dynamic/5-dynamic.Rmd`
Files and R Markdown | `6-files/6-files.Rmd`

Notebooks `3-changes/3-changes.Rmd` and `4-static/4-static.Rmd` rely on the following Shiny apps.

App | Notebook | 
---|---
 <http://wlandau.shinyapps.io/learndrakechanges> | `3-changes/3-changes.Rmd`
<http://wlandau.shinyapps.io/learndrakestatic> | `4-static/4-static.Rmd`
<http://wlandau.shinyapps.io/drakeplanner> | `4-static/4-static.Rmd`

# The `learndrake` package

The [`learndrake`](https://github.com/wlandau/learndrake) R package contains the materials of the short course. It helps students take the workshop locally if they so choose, and it helps educators and administrators host the workshop from alternative platforms.

## Installation 

You can install [`learndrake`](https://github.com/wlandau/learndrake) from GitHub.

```{r, eval = FALSE}
install.packages("remotes")
remotes::install_github("wlandau/learndrake")
```

To run the exercises locally, you will also need [TensorFlow](https://www.tensorflow.org) and [Keras](https://keras.io/).

```{r, eval = FALSE}
keras::install_keras()
# Check if the installation succeeded.
tensorflow::tf_config()
```

If you are using RStudio version 1.2.5003 and encounter [this fatal error](https://github.com/rstudio/rstudio/issues/6049), consider downgrading TensorFlow to version 1.13.1. Note: `install_keras()` silently tries to upgrade TensorFlow to version >= 2, so you will need to run it with `tensorflow = "1.13.1`.

## Usage

The functions in `learndrake` deploy and serve the workshop materials.

Function | Purpose
---|---
`save_notebooks()` | Save the `*.Rmd` notebooks to your computer.
`view_slides()` | Open the intro slides in a web browser.
`save_slides()` | Save the intro slides to your computer.
`launch_app()` | Launch a supporting Shiny app.
`save_app()` | Save the code files of a supporting Shiny app.

# Thanks

Thanks to | For
---|---
[Edgar Ruiz](https://github.com/edgararuiz) | Uniting `drake` and `keras` at <https://github.com/sol-eng/tensorflow-w-r> and providing valuable advice on the construction of the workshop.
[Matt Dancho](https://github.com/mdancho84) | Publishing the original [blog post](https://blogs.rstudio.com/tensorflow/posts/2018-01-11-keras-customer-churn/) with the workshop's underlying case study.
[Eric Nantz](https://github.com/rpodcast) | Reviewing and providing feedback on this workshop.
