---
title: "Dynamic branching"
output: html_notebook
---

# Do first

1. Navigate to the `5-dynamic-solutions/` folder.
2. Open `5-dynamic-solutions.Rproj` as an RStudio project in a new R session. (Click on `5-dynamic-solutions.Rproj` in RStudio's file manager.)
3. Check that your working directory is correct. It should be `5-dynamic-solutions/`.

```{r}
basename(getwd()) # Should be "5-dynamic-solutions"
```

4. Run the setup chunk below.

```{r, include = FALSE}
source("../config/options.R")
```

5. Load the packages and functions.

```{r, message = FALSE}
source("R/packages.R")
source("R/functions.R")
```

# Limitations of static branching

In static branching, the *definition* of each target can depend on the *definitions* other targets.

```{r, paged.print = FALSE}
drake_plan(
  churn_data = split_data(file_in("../data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data),
  run = target(
    test_model(act1 = act, churn_data, churn_recipe),
    transform = map(act = c("relu", "sigmoid", "softmax"))
  ),
  best_run = target(
    bind_rows(run) %>%
      filter(accuracy == max(accuracy)),
    transform = combine(run)
  ),
  best_model = target(
    train_best_model(best_run, churn_recipe),
    format = "keras"
  )
)
```

But what if the *definition* of a target depends on the *values* of other targets? Static branching does not allow this. The plan below is broken.

```{r}
broken_plan <- drake_plan(
  churn_data = split_data(file_in("../data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data),
  activations = c("relu", "sigmoid", "softmax"), # Target with activation functions
  run = target(
    test_model(act1 = act, churn_data, churn_recipe),
    # Try to use the value of one target in the definitions of others.
    transform = map(act = activations)
  ),
  best_run = target(
    bind_rows(run) %>%
      filter(accuracy == max(accuracy)),
    transform = combine(run)
  ),
  best_model = target(
    train_best_model(best_run, churn_recipe),
    format = "keras"
  )
)
```

```{r, paged.print = FALSE}
broken_plan
```

`test_model()` is only supposed to get a single activation function, not all three.

```{r, error = TRUE}
make(broken_plan)
```

# Dynamic branching

In dynamic branching, the *definition* of a target can depend on the *values* of other targets. Let's dynamically create a model run for each activation function.

```{r}
plan <- drake_plan(
  churn_data = split_data(file_in("../data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data),
  act = c("relu", "sigmoid", "softmax"), # A target with activation functions
  run = target(
    test_model(act1 = act, churn_data, churn_recipe),
    dynamic = map(act) # Dynamic branching
  ),
  best_run = filter(run, accuracy == max(accuracy)),
  best_model = target(
    train_best_model(best_run, churn_recipe),
    format = "keras"
  )
)
```

`drake` does not know in advance how many models runs it will perform, so the plan is more compact than it would have been with static branching.

```{r, paged.print = FALSE}
plan
```

```{r}
vis_drake_graph(plan)
```

Let's run those models.

```{r}
make(plan)
```

Each model run is now a *dynamic sub-target*.

```{r}
run_names <- subtargets(run)
run_names
```

```{r}
readd(run_names[1], character_only = TRUE)
```

A full dynamic target is a "vector" of sub-targets. `drake`'s vector semantics come from the `vctrs` R package, which generalizes the concept of a vector to data frames as well as ordinary atomic vectors. That means our `run` target is automatically a data frame.

```{r}
readd(run)
```

The command of `best_run` already assumed this.

```{r}
plan %>%
  filter(target == "best_run") %>%
  pull(command) %>%
  `[[`(1)
```

# Your turn

Define a new dynamic target with the accuracy of each model run.

```{r}
plan <- drake_plan(
  churn_data = split_data(file_in("../data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data),
  act = c("relu", "sigmoid", "softmax"),
  run = target(
    test_model(act1 = act, churn_data, churn_recipe),
    dynamic = map(act) 
  ),
  acc = target(
    run$accuracy,
    dynamic = map(run)
  ),
  best_run = filter(run, accuracy == max(accuracy)),
  best_model = target(
    train_best_model(best_run, churn_recipe),
    format = "keras"
  )
)
```

Run the plan.

```{r}
make(plan)
```

The result should be a numeric vector of length 3.

```{r}
readd(acc)
```

# The trace

How do you know which `acc` value belongs to which model? Use the `.trace` argument of `map()`.

```{r}
plan <- drake_plan(
  churn_data = split_data(file_in("../data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data),
  act = c("relu", "sigmoid", "softmax"),
  run = target(
    test_model(act1 = act, churn_data, churn_recipe),
    dynamic = map(act)
  ),
  acc = target(
    run$accuracy,
    # Label each accuracy value with the corresponding activation function.
    # Note: we need to explicitly map over act.
    dynamic = map(run, act, .trace = act)
  ),
  best_run = filter(run, accuracy == max(accuracy)),
  best_model = target(
    train_best_model(best_run, churn_recipe),
    format = "keras"
  )
)
```

Run the plan.

```{r}
make(plan)
```

`readd()` still shows the same result.

```{r}
readd(acc)
```

But each element now has a trace.

```{r}
read_trace("act", acc)
```

# Dynamic cross

The dynamic `cross()` is similar to the static one. Below, create a model run for each combination of `act` and `units`.

```{r}
plan <- drake_plan(
  churn_data = split_data(file_in("../data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data),
  act = c("relu", "sigmoid", "softmax"),
  units = c(16, 32), # New target with the size of the first layer.
  run = target(
    # Using different layer sizes.
    test_model(act1 = act, units1 = units, churn_data, churn_recipe),
    dynamic = cross(act, units) # Your turn: cross() over both act and units.
  ),
  best_run = filter(run, accuracy == max(accuracy)),
  best_model = target(
    train_best_model(best_run, churn_recipe),
    format = "keras"
  )
)
```

We should have six model runs now.

```{r}
make(plan)
```

Our dynamic target should have six rows, one for each combination of `act1` and `units1`.

```{r}
readd(run)
```

# Dynamic group

`group()` can chop up dynamic and static targets into groups. It is a mechanism for both splitting and aggregation. Using the `.by` argument of `group()`, we can group the runs by each activation function. Note: `.by` needs to be the same length as the target being grouped. Complete the plan below.

```{r}
plan <- drake_plan(
  churn_data = split_data(file_in("../data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data),
  act = c("relu", "sigmoid", "softmax"),
  units = c(16, 32),
  run = target(
    test_model(act1 = act, units1 = units, churn_data, churn_recipe),
    dynamic = cross(act, units)
  ),
  run_act = run$act1, # Needed for .by in group() below.
  grouped_runs = target(
    run,
    dynamic = group(run, run_act, .by = run_act)
  )
)
```

Run the workflow.

```{r}
make(plan)
```

Notice now that we have three `best_run` sub-targets, each with the two rows for a given value of `act1`.

```{r}
grouped_runs_names <- subtargets(grouped_runs)
grouped_runs_names
```

```{r}
readd(grouped_runs_names[1], character_only = TRUE)
```

```{r}
readd(grouped_runs_names[2], character_only = TRUE)
```

```{r}
readd(grouped_runs_names[3], character_only = TRUE)
```

A downstream `map()` lets us train the best model for each activation function.

```{r}
plan <- drake_plan(
  churn_data = split_data(file_in("../data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data),
  act = c("relu", "sigmoid", "softmax"),
  units = c(16, 32),
  run = target(
    test_model(act1 = act, units1 = units, churn_data, churn_recipe),
    dynamic = cross(act, units)
  ),
  run_act = run$act1,
  best_run = target(
    filter(run, accuracy == max(accuracy)),
    dynamic = group(run, run_act, .by = run_act)
  ),
  best_run_act = best_run$act1,
  best_model = target(
    train_best_model(best_run, churn_recipe),
    format = "keras",
    dynamic = map(best_run, best_run_act, .trace = best_run_act)
  )
)
```

Let's run those models.

```{r}
make(plan)
```

Our `best_run` target has three rows because we filtered `run` after grouping it by activation function.

```{r}
readd(best_run)
```

Thanks to the trace, we know which `best_model` sub-target has which activation function.

```{r}
read_trace("best_run_act", best_model)
```

`best_model` itself is a dynamic target, a list of three trained Keras models.

```{r}
readd(best_model)
```
