---
title: "Dynamic reports and literate programming"
output: html_notebook
---

```{r, include = FALSE}
# Set your working directory to 6-reports/.
# You may have to copy and paste this line into your console:
setwd(file.path(rprojroot::find_rstudio_root_file(), "6-reports"))
source("../config/options.R")
```

# R Markdown and knitr

In `drake`, R Markdown and `knitr` reports serve as tiny pieces of the larger overarching pipeline. Their job is to annotate and explain targets defined elsewhere in the plan. They should leverage existing results and do almost no computation of their own. 

To declare a `knitr` file in a `drake` plan, use the special `knitr_in()` function. `knitr_in()` is a variant of `file_in()` that tells `drake` to scan active code chunks for dependencies.

```{r, paged.print = FALSE}
drake_plan(
  report_step = rmarkdown::render(
    input = knitr_in("your-report.Rmd"),
    output_file = file_out("your-report.html"),
    quiet = TRUE
  )
)
```

Inside the report itself, use `loadd()` and `readd()` to refer to targets. Not only does this establish the dependencies of the report, it also lets you run the report on its own (e.g. the "Knit" button in the RStudio IDE) as long as you have a `.drake/` cache from a previous `make()`.

# Exercise: documenting customer churn

## Setup

Let's use `churn-results.Rmd` report to show the results of our customer churn analysis. To prepare, do the following.

1. Open `R/plan.R` and add a `report_step` target to the plan (see above). It should call `rmarkdown::render()` with `knitr_in()` on the input and `file_out()` on the output file.
2. Open `churn-results.Rmd` and add a new active code chunk with `readd(metrics)`.

Now, set up the `drake` pipeline and visualize the dependency graph.

```{r, message = FALSE}
source("R/packages.R")
source("R/functions.R")
source("R/plan.R")
config <- drake_config(plan)
vis_drake_graph(config)
```

Your dependency graph should look something like this.

```{r}
readRDS("img/graph.rds")
```

`deps_knitr` should show `conf_model_16` and `metrics` as dependencies.

```{r, paged.print = FALSE}
deps_knitr("churn-results.Rmd")
```

`deps_target()` should show `rmarkdown::render()`, `conf_model_16`, `metrics`, `churn-results.html`, and `churn-results.Rmd` as dependencies.

```{r, paged.print = FALSE}
deps_target(report_step, config)
```

## Execution

Now, run the pipeline.

```{r}
make(plan)
```

You should see `churn-results.html` in the output. Open it to verify that the output is correct. You should see a confusion matrix and a plot of performance metrics.

## Iteration

Edit on the report and compile it as you would normally.

1. Open `churn-results.Rmd` in the RStudio IDE and add prose to summarize the performance metrics. Write about the conclusions you can draw.
2. Press the "Knit" button to re-render the HTML report to your heart's content.

Now, go back to the `drake` pipeline. The `report_step` target should be out of date because you worked on it.

```{r}
outdated(config)
```

```{r}
vis_drake_graph(config)
```

For production, use `make()` to re-synchronize the report with the rest of the pipeline.

```{r}
make(plan)
```

```{r}
outdated(config)
```

```{r}
vis_drake_graph(config)
```
