---
title: "External files and R Markdown"
output: html_notebook
---

# Instructions

1. Navigate to the `6-files/` folder.
2. Open `6-files.Rproj` as an RStudio project in a new R session. (Click on `6-files.Rproj` in RStudio's file manager.)
3. Check that your working directory is correct. It should be `6-files/`.

```{r}
basename(getwd()) # Should be "6-files"
```

4. Run the setup chunk below.

```{r, include = FALSE}
source("../config/options.R")
```

5. Load your packages and functions.

```{r, message = FALSE}
source("R/packages.R")
source("R/functions.R")
```

6. Read the notebook below and run the code chunks along the way. Look out for comments with "YOUR TURN". Those are places where you will need to write code. Feel free to peek at `6-files-solutions/6-files-solutions.Rmd` if you get stuck.

# Reproducible file management

Some targets depend on external files. When an important file changes, we want `make()` to rerun all the affected targets. That is why we wrote `file_in("../data/customer_churn.csv")` in our previous plans. This notebook explores functions `file_in()`, `file_out()`, and `knitr_in()`, and demonstrates how they help keep `drake` workflows up to date.

# Input and output files.

For demonstration purposes, let's store all our models as external output files and then read them back in to compute test accuracy. Our initial plan has problems.

```{r}
broken_plan <- drake_plan(
  churn_data = split_data(file_in("../data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data),
  model_relu = save_model_hdf5(
    train_model(act1 = "relu", churn_recipe),
    "model_relu.h5"
  ),
  model_sigmoid = save_model_hdf5(
    train_model(act1 = "sigmoid", churn_recipe),
    "model_sigmoid.h5"
  ),
  test_relu = test_accuracy(
    churn_data,
    churn_recipe,
    load_model_hdf5("model_relu.h5")
  ),
  test_sigmoid = test_accuracy(
    churn_data,
    churn_recipe,
    load_model_hdf5("model_sigmoid.h5")
  )
)
```

Clearly, `test_relu` should depend on `model_relu` and `test_sigmoid` should depend on `model_sigmoid`. However, these dependency relationships are missing from the graph. `drake` misunderstands the workflow and cannot reliably maintain it in its current form.

```{r}
# Like vis_drake_graph(), but without functions or target status colors.
plot(broken_plan)
```

Your turn: use `file_in()` and `file_out()` to label the HDF5 models as input and output files. 

```{r}
plan <- drake_plan(
  # Hint: here is an existing example of file_in().
  churn_data = split_data(file_in("../data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data),
  model_relu = save_model_hdf5(
    train_model(act1 = "relu", churn_recipe),
    "model_relu.h5" # YOUR TURN: put "model_relu.h5" inside file_out().
  ),
  model_sigmoid = save_model_hdf5(
    train_model(act1 = "sigmoid", churn_recipe),
    "model_sigmoid.h5" # YOUR TURN: put "model_sigmoid.h5" inside file_out().
  ),
  test_relu = test_accuracy(
    churn_data,
    churn_recipe,
    # YOUR TURN: put the file name inside file_in().
    load_model_hdf5("model_relu.h5")
  ),
  test_sigmoid = test_accuracy(
    churn_data,
    churn_recipe,
    # YOUR TURN: put the file name inside file_in().
    load_model_hdf5("model_sigmoid.h5")
  )
)
```

Now, the `test_*` targets should be directly downstream of the `model_*` targets.

```{r}
plot(plan)
```

Let's run that plan.

```{r}
make(plan)
```

Now, suppose a model file gets corrupted.

```{r}
writeLines("garbage", "model_relu.h5") # Oh no!
```

`file_in()` and `file_out()` save us. The target that produced the file and all downstream targets are no longer valid.

```{r}
outdated(plan)
```

```{r}
vis_drake_graph(plan)
```

`make(plan)` runs only the affected targets.

```{r}
make(plan)
```

# Limitations of file_in() and friends

`drake` needs to understand your `file_in()` statements without having to run the code, so you should always apply literal strings to `file_in()` and friends.

```{r}
good_plan <- drake_plan(
  churn_data = split_data(file_in("../data/customer_churn.csv")) # Literal path
)

vis_drake_graph(good_plan)
```

If you supply a symbol name, `drake` cannot detect the file.

```{r}
path <- "../data/customer_churn.csv"

broken_plan <- drake_plan(
  churn_data = split_data(file_in(path))
)

broken_plan

vis_drake_graph(broken_plan) # The file is missing!
```

Tidy evaluation with `!!` works around this problem by directly inserting the contents of the symbol when the plan gets created.

```{r}
path <- "../data/customer_churn.csv"

broken_plan <- drake_plan(
  churn_data = split_data(file_in(!!path)) # Use tidy evaluation
)

broken_plan

vis_drake_graph(broken_plan) # The file is missing!
```

`file_in()` and friends must literally wrap around the strings you supply. Pipe operators like `magrittr`'s `%>%` can get in the way of this.

```{r}
broken_plan <- drake_plan(
  churn_data = "../data/customer_churn.csv" %>%
    file_in() %>% # drake's static code analyzer thinks file_in() is empty.
    split_data()
)

vis_drake_graph(broken_plan) # The file is missing!
```

In addition, `file_out()` is incompatible with dynamic branching. And if you use `file_in("your_file")` for a dynamic target, then all the sub-targets will depend on "your_file".

# Dynamic files

To overcome the limitations of `file_in()` and friends, `drake` supports dynamic files. With dynamic files, `drake` can track changes to local files without knowing the names of those files in advance. This is a more flexible alternative to `file_out()` and `file_in()`, and it is fully compatible with dynamic branching. To use dynamic files, there are three rules:

1. Set format = "file" in `target()` within `drake_plan()`.
2. Return the paths to local files from the target.
3. To link targets together in dependency relationships, reference target names and not literal character strings.

Here is an example of a plan that uses dynamic files. Notice the usage of `format = "file"` below.

```{r}
plan <- drake_plan(
  data_file = target(
    "../data/customer_churn.csv",
    # Replaces file_in() in this case.
    # Could also be used to replace file_out().
    format = "file"
  ),
  churn_data = split_data(data_file) # Updates when the CSV file changes.
)

make(plan)
```

YOUR TURN: remove the last data row in `../data/customer_churn.csv` and run `make(plan)` again. Both `data_file` and `churn_data` should automatically rerun.

```{r}
make(plan)
```

# Literate programming

R Markdown and `knitr` are not designed for the intense computation that `drake` workflows face. They are not pipeline tools, and they should do as little work as possible. However, they are useful components of `drake` pipelines, especially when they communicate and annotate hard-won results from previous targets. To connect an R Markdown or `knitr` report to `drake`, there are three steps.

1. In the plan, use `knitr_in()` to mark the source file of your report (the `*.Rmd` or `*.Rnw` file). 
2. In the plan, use `file_out()` to mark the rendered output (the `*.html` or `*.pdf` file).
3. In the active code chunks of the report itself, use `drake`'s `loadd()` and `readd()` functions to explicitly mark targets that the report depends on. Not only does this tell `drake` which targets the report depends on, it also allows you to run the report by itself without calling `make()`.

# Your turn

1. In the R Markdown file `results.Rmd`, write an active code chunk with `readd(best_model)`. That tells `drake` that the report depends on `results.Rmd`
2. In the plan below, use `knitr_in()` and `file_out()` to mark the input and output files to `rmarkdown::render()`, respectively.

```{r}
plan <- drake_plan(
  churn_data = split_data(file_in("../data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data),
  act = c("relu", "sigmoid", "softmax"),
  run = target(
    test_model(act1 = act, churn_data, churn_recipe),
    dynamic = map(act)
  ),
  best_run = head(top_n(run, 1, accuracy), 1),
  best_model = target(
    train_best_model(best_run, churn_recipe),
    format = "keras"
  ),
  report_step = rmarkdown::render(
    "results.Rmd", # YOUR TURN: enclose "results.Rmd" inside knitr_in().
    output_file = "results.html", # YOUR TURN: put "results.html" in file_out().
    quiet = TRUE
  )
)
```

Thanks to `knitr_in()` and friends, the `report_step` target should depend on `run`, `best_model`, `"results.Rmd"`, and `"results.html"`.

```{r}
deps_target(report_step, plan)
```

```{r}
vis_drake_graph(plan)
```

Let's run the workflow.

```{r}
make(plan)
```

Everything should be up to date now.

```{r}
outdated(plan)
```

Open `results.html` and look at the output. You should see quick summaries of hard-won targets.

# Your turn: edit the R Markdown report

Now, open `results.Rmd` in RStudio and add any comments you want. If you like, click the "Knit" button in RStudio to re-render the report. Afterwards, the `report_step` target should be outdated.

```{r}
outdated(plan)
```

When you are finished editing the report, rerun `make(plan)` to bring it up to date in the workflow.

```{r}
make(plan)
```
