---
title: "Advanced plans"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(drake)
library(DT)
library(learnr)
library(praise)
library(styler)
library(tidyverse)
library(visNetwork)
options(
  drake_make_menu = FALSE,
  drake_clean_menu = FALSE,
  warnPartialMatchArgs = FALSE,
  crayon.enabled = FALSE,
  readr.show_progress = FALSE,
  tibble.print_max = 25
)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE
)
laud <- function() {
  praise("${Exclamation}! ${Adverb} ${adjective} answer.")
}
drake_checker <- function(
  label,
  user_code,
  solution_code,
  check_code,
  envir_result,
  evaluate_result,
  envir_prep,
  ...
) {
  out <- eval(parse(text = user_code))
  exp <- eval(parse(text = check_code))
  ans <- same_plan(out, exp)
  msg <- ifelse(ans, laud(), "Try again.")
  list(message = msg, correct = ans, location = "append")
}
tutorial_options(exercise.checker = drake_checker)
safe_deparse <- function (x, collapse = "\n") {
  paste(deparse(x, control = c("keepInteger", "keepNA")), collapse = collapse)
}
deparse_commands <- function (x) {
  unlist(lapply(x, safe_deparse, collapse = " "))
}
deparse_plan <- function(plan) {
  plan$command <- deparse_commands(plan$command)
  plan
}
same_plan <- function (out, exp) {
  out <- deparse_plan(out)
  exp <- deparse_plan(exp)
  out <- out[order(out$target), ]
  exp <- exp[order(exp$target), ]
  all(out$target == exp$target & out$command == exp$command)
}
dp_graph <- function(plan) {
  config <- drake_config(
    plan,
    cache = storr::storr_environment(),
    session_info = FALSE,
    history = FALSE
  )
  vis_drake_graph(
    config,
    main = "",
    hover = TRUE,
    from = file_store("data/customer_churn.csv")
  )
}
dp_table <- function(plan) {
  DT::datatable(deparse_plan(plan), rownames = FALSE)
}
```

## Instructions

Repair the unfinished [drake plans](https://books.ropensci.org/drake/plans.html#large-plans) in the following exercises. Optional: use [drakeplanner](https://wlandau.shinyapps.io/drakeplanner) to help write and check your plans.

```{r q0}
question(
  "Okay?",
  correct = laud(),
  incorrect = "Let's talk.",
  allow_retry = TRUE,
  random_answer_order = TRUE,
  answer("Yes", correct = TRUE),
  answer("No"),
  answer("You lost me way back at the beginning."),
  answer("I cannot find `drakeplanner` or `4-plans.Rmd`."),
  answer("Wait, what is a drake plan?")
)
```

## Exercise 1

Write a plan that tries different layer sizes. For each model, `units1` must equal `units2`.

```{r e1, exercise = TRUE, exercise.lines = 24}
plan <- drake_plan(
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(rec, units1 = u1, units2 = u2),
    format = "keras",
    transform = map(
      u1 = c(16, 32, 64),
      # Your turn: set the units of the second layer to the same ones as u1.
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf)
  )
)
```

Expected [drakeplanner](https://wlandau.shinyapps.io/drakeplanner) output:

```{r}
expected1 <- drake_plan(
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(rec, units1 = u1, units2 = u2),
    format = "keras",
    transform = map(
      u1 = c(16, 32, 64),
      u2 = c(16, 32, 64)
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf)
  )
)
```

```{r}
dp_graph(expected1)
```

```{r}
dp_table(expected1)
```

```{r e1-check}
drake_plan(
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(rec, units1 = u1, units2 = u2),
    format = "keras",
    transform = map(
      u1 = c(16, 32, 64),
      u2 = c(16, 32, 64)
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf)
  )
)
```

## Exercise 2

Now, use `cross()` to create a new model for each combination of `units1` and `units2`

```{r e2, exercise = TRUE, exercise.lines = 24}
plan <- drake_plan(
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(rec, units1 = u1, units2 = u2),
    format = "keras",
    transform = map( # Your turn: change map() to cross().
      u1 = c(16, 32, 64),
      # Your turn: set the units of the second layer to the same ones as u1.
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf)
  )
)
```

Expected [drakeplanner](https://wlandau.shinyapps.io/drakeplanner) output:

```{r}
expected2 <- drake_plan(
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(rec, units1 = u1, units2 = u2),
    format = "keras",
    transform = cross(
      u1 = c(16, 32, 64),
      u2 = c(16, 32, 64)
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf)
  )
)
```

```{r}
dp_graph(expected2)
```

```{r}
dp_table(expected2)
```

```{r e2-check}
drake_plan(
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(rec, units1 = u1, units2 = u2),
    format = "keras",
    transform = cross(
      u1 = c(16, 32, 64),
      u2 = c(16, 32, 64)
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf)
  )
)
```

## Exercise 3

Recall: with `!!`, you can generate commands programmatically.

```{r, paged.print = FALSE, echo = TRUE}
xs <- seq_len(100)
drake_plan(
  y = target(
    f(x),
    transform = map(x = !!xs)
  )
)
```

Try it with our deep learning plan. Use `!!` to insert lots of models with different values of `units1`.

```{r e3, exercise = TRUE, exercise.lines = 25}
my_units1 <- seq(8, 64, by = 1) # Use these values.

plan <- drake_plan(
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(rec, units1 = u1),
    format = "keras",
    transform = map(
      # Your turn: use !! to insert the values of my_units1 in for u1.
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf)
  )
)
```

Expected [drakeplanner](https://wlandau.shinyapps.io/drakeplanner) output:

```{r}
my_units1 <- seq(8, 64, by = 1) # Use these values.

expected3 <- drake_plan(
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(rec, units1 = u1),
    format = "keras",
    transform = map(
      u1 = !!my_units1
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf)
  )
)
```

```{r}
dp_graph(expected3)
```

```{r}
dp_table(expected3)
```

```{r e3-check}
my_units1 <- seq(8, 64, by = 1)

drake_plan(
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(rec, units1 = u1),
    format = "keras",
    transform = map(
      u1 = !!my_units1
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf)
  )
)
```

## Exercise 4

Now that was too many targets to visualize! Let's scale down with `max_expand`.

```{r, paged.print = FALSE, echo = TRUE}
xs <- seq_len(100)
drake_plan(
  y = target(f(x), transform = map(x = !!xs)),
  max_expand = 4
)
```

Try it with our deep learning plan. Set `max_expand = 4` in `drake_plan()`.

```{r e4, exercise = TRUE, exercise.lines = 25}
my_units1 <- seq(8, 64, by = 1) # Use these values.

plan <- drake_plan(
  # Your turn: set max_expand to 4.
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(rec, units1 = u1),
    format = "keras",
    transform = map(
      # Your turn: use !! to insert the values of my_units1 in for u1.
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf)
  )
)
```

Expected [drakeplanner](https://wlandau.shinyapps.io/drakeplanner) output:

```{r}
my_units1 <- seq(8, 64, by = 1) # Use these values.

expected4 <- drake_plan(
  max_expand = 4,
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(rec, units1 = u1),
    format = "keras",
    transform = map(
      u1 = !!my_units1
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf)
  )
)
```

```{r}
dp_graph(expected4)
```

```{r}
dp_table(expected4)
```

```{r e4-check}
my_units1 <- seq(8, 64, by = 1)

drake_plan(
  max_expand = 4,
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(rec, units1 = u1),
    format = "keras",
    transform = map(
      u1 = !!my_units1
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf)
  )
)
```


## Exercise 5

You can make a custom grid of grouping variables for `map()` and `cross()`. Note the use of `!!`.

```{r, paged.print = FALSE, echo = TRUE}
grid <- data.frame(x = c(1, 1, 2), y = c(3, 4, 4))
drake_plan(z = target(f(x, y), transform = map(.data = !!grid)))
```

Try it with our deep learning plan. Use a custom grid of layer 1 model settings: `"relu"` activation with 32 units, `"relu"` activation with 64 units, and `"sigmoid"` activation with 64 units.

```{r e5, exercise = TRUE, exercise.lines = 30}
# This is our grid.
my_grid <- tibble(
  my_units1 = c(32, 64, 64),
  my_act1 = c("relu", "relu", "sigmoid")
)

# And this is our plan.
plan <- drake_plan(
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(rec, units1 = my_units1, act1 = my_act1),
    format = "keras",
    transform = map(
      ... = # Use !! to apply the grid of settings.
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf)
  )
)
```

Expected [drakeplanner](https://wlandau.shinyapps.io/drakeplanner) output:

```{r}
my_grid <- tibble(
  my_units1 = c(32, 64, 64),
  my_act1 = c("relu", "relu", "sigmoid")
)

expected5 <- drake_plan(
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(rec, units1 = my_units1, act1 = my_act1),
    format = "keras",
    transform = map(
      .data = !!my_grid
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf)
  )
)
```

```{r}
dp_graph(expected5)
```

```{r}
dp_table(expected5)
```

```{r e5-check}
my_grid <- tibble(
  my_units1 = c(32, 64, 64),
  my_act1 = c("relu", "relu", "sigmoid")
)

drake_plan(
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(rec, units1 = my_units1, act1 = my_act1),
    format = "keras",
    transform = map(
      .data = !!my_grid
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf)
  )
)
```


## Exercise 6

Now, try using `cross()` instead of `map()` when you apply the grid. (Note: we have a different grid now.)

```{r e6, exercise = TRUE, exercise.lines = 28}
my_grid <- tibble(
  my_units1 = c(16, 32, 64),
  my_act1 = c("relu", "sigmoid", "softmax")
)

plan <- drake_plan(
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(rec, units1 = my_units1, act1 = my_act1),
    format = "keras",
    transform = map( # Use cross() instead of map()
      ... = # Use !! to apply the grid of settings.
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf)
  )
)
```

```{r}
my_grid <- tibble(
  my_units1 = c(16, 32, 64),
  my_act1 = c("relu", "sigmoid", "softmax")
)

expected6 <- drake_plan(
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(rec, units1 = my_units1, act1 = my_act1),
    format = "keras",
    transform = cross(
      .data = !!my_grid
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf)
  )
)
```

```{r e6-check}
my_grid <- tibble(
  my_units1 = c(16, 32, 64),
  my_act1 = c("relu", "sigmoid", "softmax")
)

drake_plan(
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(rec, units1 = my_units1, act1 = my_act1),
    format = "keras",
    transform = cross(
      .data = !!my_grid
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf)
  )
)
```

Use [drakeplanner](https://wlandau.shinyapps.io/drakeplanner) to visualize the plan.

```{r q6}
question(
  "How many models did you get?",
  correct = laud(),
  incorrect = "Don't worry, you'll kick that football someday.",
  allow_retry = TRUE,
  answer("I got 9 models.", correct = TRUE),
  answer("I got 3 models."),
  answer("I got 1 model."),
  answer("I got a rock.")
)
```

## Exercise 7

Now, let's talk about `combine()`. With the `.by` argument of `combine()`, you can create grouped summaries of targets.

```{r, echo = TRUE, paged.print = FALSE}
drake_plan(
  z = target(
    f(x, y),
    transform = cross(x = c(1, 2), y = c(3, 4))
  ),
  w = target(
    bind_rows(z),
    transform = combine(z, .by = x)
  )
)
```

In our deep learning plan, create a `metrics_*` target for each **activation function**.

```{r e7, exercise = TRUE, exercise.lines = 31}
my_grid <- tibble(
  my_units1 = c(16, 32, 64),
  my_act1 = c("relu", "sigmoid", "softmax")
)

plan <- drake_plan(
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(rec, units1 = my_units1, act1 = my_act1),
    format = "keras",
    transform = map( # Use cross() instead of map().
      ... = # Use !! to apply the grid of settings.
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(
      conf,
      # Use .by to create a metrics_* target for each activation function.
    )
  )
)
```

Expected [drakeplanner](https://wlandau.shinyapps.io/drakeplanner) output:

```{r}
my_grid <- tibble(
  my_units1 = c(16, 32, 64),
  my_act1 = c("relu", "sigmoid", "softmax")
)

expected7 <- drake_plan(
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(rec, units1 = my_units1, act1 = my_act1),
    format = "keras",
    transform = cross(
      .data = !!my_grid
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf, .by = my_act1)
  )
)
```

```{r}
dp_graph(expected7)
```

```{r}
dp_table(expected7)
```

```{r e7-check}
my_grid <- tibble(
  my_units1 = c(16, 32, 64),
  my_act1 = c("relu", "sigmoid", "softmax")
)

drake_plan(
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(rec, units1 = my_units1, act1 = my_act1),
    format = "keras",
    transform = cross(
      .data = !!my_grid
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf, .by = my_act1)
  )
)
```


## Exercise 8

Now, create a `metrics_*` target for each **combination of `units1` and `units2`** (in that order).

```{r e8, exercise = TRUE, exercise.lines = 35}
my_grid <- tibble(
  my_act1 = c("relu", "sigmoid", "softmax"),
  my_units1 = c(16, 32, 64),
  my_units2 = c(16, 32, 64)
)

plan <- drake_plan(
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(
      rec,
      units1 = my_units1,
      units2 = my_units2,
      act1 = my_act1
    ),
    format = "keras",
    transform = cross(
      .data = !!my_grid
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf, .by = c(...)) # What goes in place of the dots?
  )
)
```

Expected [drakeplanner](https://wlandau.shinyapps.io/drakeplanner) output:

```{r}
my_grid <- tibble(
  my_act1 = c("relu", "sigmoid", "softmax"),
  my_units1 = c(16, 32, 64),
  my_units2 = c(16, 32, 64)
)

expected8 <- drake_plan(
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(
      rec,
      units1 = my_units1,
      units2 = my_units2,
      act1 = my_act1
    ),
    format = "keras",
    transform = cross(
      .data = !!my_grid
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf, .by = c(my_units1, my_units2))
  )
)
```

```{r}
dp_graph(expected8)
```

```{r}
dp_table(expected8)
```

```{r e8-check}
my_grid <- tibble(
  my_act1 = c("relu", "sigmoid", "softmax"),
  my_units1 = c(16, 32, 64),
  my_units2 = c(16, 32, 64)
)

drake_plan(
  data = read_csv(
    file_in("data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
  rec = prepare_recipe(data),
  model = target(
    train_model(
      rec,
      units1 = my_units1,
      units2 = my_units2,
      act1 = my_act1
    ),
    format = "keras",
    transform = cross(
      .data = !!my_grid
    )
  ),
  conf = target(
    confusion_matrix(data, rec, model),
    transform = map(model)
  ),
  metrics = target(
    compare_models(conf),
    transform = combine(conf, .by = c(my_units1, my_units2))
  )
)
```
