---
title: "Static branching"
subtitle: "Short code for long plans"
output:
  learnr::tutorial:
    df_print: default
runtime: shiny_prerendered
---

```{r setup, include = FALSE}
library(drake)
library(DT)
library(learnr)
library(styler)
library(tidyverse)
library(visNetwork)
options(
  drake_make_menu = FALSE,
  drake_clean_menu = FALSE,
  warnPartialMatchArgs = FALSE,
  crayon.enabled = FALSE,
  readr.show_progress = FALSE,
  tibble.print_max = 25
)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE
)
drake_checker <- function(
  label,
  user_code,
  solution_code,
  check_code,
  envir_result,
  evaluate_result,
  envir_prep,
  ...
) {
  out <- eval(parse(text = user_code))
  exp <- eval(parse(text = check_code))
  ans <- same_plan(out, exp)
  msg <- ifelse(ans, random_praise(), "Try again.")
  list(message = msg, correct = ans, location = "append")
}
tutorial_options(
  exercise.checker = drake_checker,
  exercise.cap = ""
)
safe_deparse <- function (x, collapse = "\n") {
  paste(deparse(x, control = c("keepInteger", "keepNA")), collapse = collapse)
}
deparse_commands <- function (x) {
  unlist(lapply(x, safe_deparse, collapse = " "))
}
deparse_plan <- function(plan) {
  plan$command <- deparse_commands(plan$command)
  plan
}
same_plan <- function (out, exp) {
  out <- deparse_plan(out)
  exp <- deparse_plan(exp)
  out <- out[order(out$target), ]
  exp <- exp[order(exp$target), ]
  all(out$target == exp$target & out$command == exp$command)
}
dp_graph <- function(plan) {
  info <- drake_graph_info(
    plan = plan,
    cache = storr::storr_environment(),
    session_info = FALSE,
    history = FALSE,
    from = file_store("data/customer_churn.csv")
  )
  render_drake_graph(
    info,
    width = "100%",
    hover = TRUE,
    main = "",
    navigationButtons = FALSE,
    ncol_legend = 0
  )
}
dp_table <- function(plan) {
  DT::datatable(
    deparse_plan(plan),
    rownames = FALSE,
    autoHideNavigation = TRUE,
    class = "cell-border",
    options = list(dom = "tip", searchPanes = FALSE, bInfo = FALSE)
  )
}
```

## Problems with large plans

In real life, workflows grow and `drake` plans get cumbersome. To seriously model customer churn, we need to test many more models.

```r
drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run_relu = test_model(act1 = "relu", churn_data, churn_recipe),
  run_elu = test_model(act1 = "elu", churn_data, churn_recipe),
  run_selu = test_model(act1 = "selu", churn_data, churn_recipe),
  run_hard_sigmoid = test_model(act1 = "hard_sigmoid", churn_data, churn_recipe),
  run_linear = test_model(act1 = "linear", churn_data, churn_recipe),
  run_sigmoid = test_model(act1 = "sigmoid", churn_data, churn_recipe),
  run_softmax = test_model(act1 = "softmax", churn_data, churn_recipe),
  run_softplus = test_model(act1 = "softplus", churn_data, churn_recipe),
  run_softsign = test_model(act1 = "softsign", churn_data, churn_recipe),
  run_tanh = test_model(act1 = "tanh", churn_data, churn_recipe),
  run_exponential = test_model(act1 = "exponential", churn_data, churn_recipe)
)
```

```{r problem}
question(
  "Anything wrong with this plan?",
  correct = random_praise(),
  incorrect = "Let's talk.",
  allow_retry = TRUE,
  answer("Too much manual typing!", correct = TRUE),
  answer("But I like typing..."),
  answer("Wait, what is a drake plan?")
)
```

## Static branching

To avoid excessive typing, `drake` has a special [static branching](https://books.ropensci.org/drake/static.html) interface. Below, `transform = map()` declares a new model run for every activation function.

```{r, echo = TRUE, paged.print = FALSE}
drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    test_model(act1 = act, churn_data, churn_recipe),
    transform = map(
      act = c(
        "elu", "selu", "hard_sigmoid", "linear",
        "softplus", "softsign", "tanh", "exponential"
      )
    )
  )
)
```

```{r convenient}
question(
  "Sound convenient?",
  correct = random_praise(),
  incorrect = "Let's talk.",
  allow_retry = TRUE,
  answer("Yes.", correct = TRUE),
  answer("I am not convinced.")
)
```

## A larger map

A single `map()` can take multiple grouping variables. Let's supply a different layer size for each activation function. Here is the plan we want.

```{r}
expected <- drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    test_model(act1 = act, units1 = units, churn_data, churn_recipe),
    transform = map(
      act = c(
        "elu", "selu", "hard_sigmoid", "linear",
        "softplus", "softsign", "tanh", "exponential"
      ),
      units = c(16, 17, 18, 19, 20, 21, 22, 23)
    )
  )
)
```

```{r}
dp_table(expected)
```

The graph should look like this.

```{r}
dp_graph(expected)
```

Create the above plan in the text editor below. Use the [drakeplanner](https://wlandau.shinyapps.io/drakeplanner) app to help you. When you are ready, click the "Submit Answer" button to the right of the editor.

```{r largermap, exercise = TRUE, echo = FALSE, exercise.lines = 18, paged.print = FALSE}
drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    # Note: we are now using the units1 argument of test_model().
    test_model(act1 = act, units1 = units, churn_data, churn_recipe),
    transform = map(
      act = c(
        "elu", "selu", "hard_sigmoid", "linear",
        "softplus", "softsign", "tanh", "exponential"
      ),
      units = ??? # Write out a numeric vector by hand
      # with literal elements 16, 17, 18, 19, 20, 21, 22, and 23.
      # Shortcuts like 16:23 and seq(16, 23, by = 1) do not work here.
      # Later exercises explain why and give compact alternatives.
    )
  )
)
```

```{r largermap-hint-1}
units = c(16, 17, 18, 19, 20, 21, 22, 23)
```

```{r largermap-hint-2}
# The next hint has the complete solution.
```

```{r largermap-hint-3}
drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    test_model(act1 = act, units1 = units, churn_data, churn_recipe),
    transform = map(
      act = c(
        "elu", "selu", "hard_sigmoid", "linear",
        "softplus", "softsign", "tanh", "exponential"
      ),
      units = c(16, 17, 18, 19, 20, 21, 22, 23)
    )
  )
)
```

```{r largermap-check}
drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    test_model(act1 = act, units1 = units, churn_data, churn_recipe),
    transform = map(
      act = c(
        "elu", "selu", "hard_sigmoid", "linear",
        "softplus", "softsign", "tanh", "exponential"
      ),
      units = c(16, 17, 18, 19, 20, 21, 22, 23)
    )
  )
)
```

## Map over symbols

Static branching is all about [symbols and expressions](https://adv-r.hadley.nz/expressions.html). `transform = map(fun_run = c(good_run, bad_run, benchmark_run)` tells `drake_plan()` to find the symbol `fun_run` and replace it with `good_run`, then `bad_run`, and then `benchmark_run`. This handy trick lets you `map()` over *functions*. Example:

```{r}
expected <- drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe),
    transform = map(fun_run = c(good_run, bad_run, benchmark_run))
  )
)
```

```{r}
dp_table(expected)
```

```{r}
dp_graph(expected)
```

Create the above plan. As always, use the [drakeplanner](https://wlandau.shinyapps.io/drakeplanner) app to help you.

```{r symbolmap, exercise = TRUE, exercise.lines = 9, paged.print = FALSE}
drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe),
    transform = map(???) # What goes here?
  )
)
```

```{r symbolmap-hint-1}
transform = map(fun_run = c(good_run, bad_run, benchmark_run))
```

```{r symbolmap-hint-2}
The next hint has the full solution.
```

```{r symbolmap-hint-3}
drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe),
    transform = map(fun_run = c(good_run, bad_run, benchmark_run))
  )
)
```

```{r symbolmap-check}
drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe),
    transform = map(fun_run = c(good_run, bad_run, benchmark_run))
  )
)
```

## Incorrect concise maps

`units = c(16, 17, 18, 19, 20, 21, 22, 23)` should be equivalent to `units = 16:23`, but we get the wrong answer when we try it in the plan.

```{r, echo = TRUE, paged.print = FALSE}
drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    test_model(act1 = act, units1 = units, churn_data, churn_recipe),
    transform = map(
      act = c(
        "elu", "selu", "hard_sigmoid", "linear",
        "softplus", "softsign", "tanh", "exponential"
      ),
      units = 16:23
    )
  )
)
```

```{r concisefail}
question(
  "Why does `units1` cycle between 16 and 32 only?",
  correct = random_praise(),
  incorrect = "Let's talk.",
  allow_retry = TRUE,
  random_answer_order = TRUE,
  answer("`drake_plan()` is all about symbols and expressions. It does not actually evaluate the expression `16:32`. It only sees the symbols `16` and `32`.", correct = TRUE),
  answer("This behavior is due to a bug in `drake_plan()`."),
  answer("The plan is actually correct.")
)
```

## Correct concise maps

In the plan, write `!!(16:32)` instead of just `16:32`. That way, `drake_plan()` evaluates the expression `16:32` and uses the actual values. The `!!` operator ("bang-bang") comes from [tidy evaluation](https://tidyeval.tidyverse.org/). 

```{r}
expected <- drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    test_model(act1 = act, units1 = units, churn_data, churn_recipe),
    transform = map(
      act = c(
        "elu", "selu", "hard_sigmoid", "linear",
        "softplus", "softsign", "tanh", "exponential"
      ),
      units = !!(16:23)
    )
  )
)
```

```{r}
dp_table(expected)
```

```{r}
dp_graph(expected)
```

Repair the plan below to create the plan above.

```{r bangbang, exercise = TRUE, exercise.lines = 15, paged.print = FALSE}
drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    test_model(act1 = act, units1 = units, churn_data, churn_recipe),
    transform = map(
      act = c(
        "elu", "selu", "hard_sigmoid", "linear",
        "softplus", "softsign", "tanh", "exponential"
      ),
      units = 16:23
    )
  )
)
```

```{r bangbang-hint-1}
units = !!(16:23)
```

```{r bangbang-hint-2}
The next hint has the full solution.
```

```{r bangbang-hint-3}
drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    test_model(act1 = act, units1 = units, churn_data, churn_recipe),
    transform = map(
      act = c(
        "elu", "selu", "hard_sigmoid", "linear",
        "softplus", "softsign", "tanh", "exponential"
      ),
      units = !!(16:23)
    )
  )
)
```

```{r bangbang-check}
drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    test_model(act1 = act, units1 = units, churn_data, churn_recipe),
    transform = map(
      act = c(
        "elu", "selu", "hard_sigmoid", "linear",
        "softplus", "softsign", "tanh", "exponential"
      ),
      units = !!(16:23)
    )
  )
)
```

## External grouping variables

Using `!!`, we can even supply grouping variables from outside the plan.

```{r}
act_values <- c(
  "elu", "selu", "hard_sigmoid", "linear",
  "softplus", "softsign", "tanh", "exponential"
)

unit_values <- 16:23 # No need for !! in this line.

expected <- drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    test_model(act1 = act, units1 = units, churn_data, churn_recipe),
    transform = map(
      act = !!act_values,
      units = !!unit_values
    )
  )
)
```

```{r}
dp_table(expected)
```

```{r}
dp_graph(expected)
```

Complete the plan below to create the one above.

```{r external, exercise = TRUE, exercise.lines = 18, paged.print = FALSE}
act_values <- c(
  "elu", "selu", "hard_sigmoid", "linear",
  "softplus", "softsign", "tanh", "exponential"
)

unit_values <- 16:23

drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    test_model(act1 = act, units1 = units, churn_data, churn_recipe),
    transform = map(
      act = ???, # What goes here?
      units = ??? # What goes here?
    )
  )
)
```

```{r external-hint-1}
act = !!act_values
```

```{r external-hint-2}
units = !!unit_values
```

```{r external-hint-3}
The next hint has the full solution.
```

```{r external-hint-4}
act_values <- c(
  "elu", "selu", "hard_sigmoid", "linear",
  "softplus", "softsign", "tanh", "exponential"
)

unit_values <- 16:23

drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    test_model(act1 = act, units1 = units, churn_data, churn_recipe),
    transform = map(
      act = !!act_values,
      units = !!unit_values
    )
  )
)
```

```{r external-check}
act_values <- c(
  "elu", "selu", "hard_sigmoid", "linear",
  "softplus", "softsign", "tanh", "exponential"
)

unit_values <- 16:23

drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    test_model(act1 = act, units1 = units, churn_data, churn_recipe),
    transform = map(
      act = !!act_values,
      units = !!unit_values
    )
  )
)
```

## External symbols

Using the `syms()` function from the `rlang` package, you can even define external *symbol vectors* to map over.

```{r}
function_names <- c("good_run", "bad_run", "benchmark_run")
function_syms <- rlang::syms(function_names)
expected <- drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe),
    transform = map(fun_run = !!function_syms)
  )
)
```

```{r}
dp_table(expected)
```

```{r}
dp_graph(expected)
```

Create the above plan.

```{r externalsymbols, exercise = TRUE, exercise.lines = 14, paged.print = FALSE}
function_names <- c("good_run", "bad_run", "benchmark_run")

# Create a symbol vector called function_syms using rlang::syms().

drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe),
    transform = map(???) # What goes here?
  )
)
```

```{r externalsymbols-hint-1}
function_syms <- rlang::syms(function_names)
```

```{r externalsymbols-hint-2}
transform = map(fun_run = !!function_syms)
```

```{r externalsymbols-hint-3}
The next hint has the full solution.
```

```{r externalsymbols-hint-4}
function_names <- c("good_run", "bad_run", "benchmark_run")

function_syms <- rlang::syms(function_names)

drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe),
    transform = map(fun_run = !!function_syms)
  )
)
```

```{r externalsymbols-check}
function_names <- c("good_run", "bad_run", "benchmark_run")
function_syms <- rlang::syms(function_names)
drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe),
    transform = map(fun_run = !!function_syms)
  )
)
```

## Data grids

`map()` has a `.data` argument to let you iterate over a custom grid of values. Try it out below. Note: values passed to `.data` need `!!`.

```{r}
grid <- tibble::tibble(
  fun_run = rlang::syms(c("good_run", "bad_run", "benchmark_run")),
  act_values = c("relu", "relu", "sigmoid"),
  units_values = c(16, 32, 32)
)
expected <- drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act_values, units = units_values),
    transform = map(.data = !!grid)
  )
)
```

```{r}
dp_table(expected)
```

```{r}
dp_graph(expected)
```

Create the above plan.

```{r grids, exercise = TRUE, exercise.lines = 15, paged.print = FALSE}
grid <- tibble::tibble(
  fun_run = rlang::syms(c("good_run", "bad_run", "benchmark_run")),
  act_values = c("relu", "relu", "sigmoid"),
  units_values = c(16, 32, 32)
)

drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act_values, units = units_values),
    transform = map(???) # What goes here?
  )
)
```

```{r grids-hint-1}
transform = map(.data = !!grid)
```

```{r grids-hint-2}
The next hint has the full solution.
```

```{r grids-hint-3}
grid <- tibble::tibble(
  fun_run = rlang::syms(c("good_run", "bad_run", "benchmark_run")),
  act_values = c("relu", "relu", "sigmoid"),
  units_values = c(16, 32, 32)
)

drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act_values, units = units_values),
    transform = map(.data = !!grid)
  )
)
```

```{r grids-check}
grid <- tibble::tibble(
  fun_run = rlang::syms(c("good_run", "bad_run", "benchmark_run")),
  act_values = c("relu", "relu", "sigmoid"),
  units_values = c(16, 32, 32)
)
drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act_values, units = units_values),
    transform = map(.data = !!grid)
  )
)
```

## Target names

The names of static branching targets can get quite long. Use the custom `.id` argument of `map()` to exclude the values of `fun_run` from the names, e.g. `.id = act_values` or `.id = c(act_values, unit_values)`. (`.id = FALSE` shortens the names even more.)

```{r}
grid <- tibble::tibble(
  fun_run = rlang::syms(c("good_run", "bad_run", "benchmark_run")),
  act_values = c("relu", "relu", "sigmoid"),
  units_values = c(16, 32, 32)
)

expected <- drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act_values, units = units_values),
    transform = map(.data = !!grid, .id = c(act_values, units_values))
  )
)
```

```{r}
dp_table(expected)
```

```{r}
dp_graph(expected)
```

Create the above plan. Use `act_values` and `units_values` to construct target names.

```{r names, exercise = TRUE, exercise.lines = 17, paged.print = FALSE}
grid <- tibble::tibble(
  fun_run = rlang::syms(c("good_run", "bad_run", "benchmark_run")),
  act_values = c("relu", "relu", "sigmoid"),
  units_values = c(16, 32, 32)
)

drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act_values, units = units_values),
    transform = map(
      .data = !!grid,
      .id = c(???) # What goes here?
    )
  )
)
```

```{r names-hint-1}
transform = map(.data = !!grid, .id = c(act_values, units_values))
```

```{r names-hint-2}
The next hint has the full solution.
```

```{r names-hint-3}
grid <- tibble::tibble(
  fun_run = rlang::syms(c("good_run", "bad_run", "benchmark_run")),
  act_values = c("relu", "relu", "sigmoid"),
  units_values = c(16, 32, 32)
)

drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act_values, units = units_values),
    transform = map(.data = !!grid, .id = c(act_values, units_values))
  )
)
```

```{r names-check}
grid <- tibble::tibble(
  fun_run = rlang::syms(c("good_run", "bad_run", "benchmark_run")),
  act_values = c("relu", "relu", "sigmoid"),
  units_values = c(16, 32, 32)
)
drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act_values, units = units_values),
    transform = map(.data = !!grid, .id = c(act_values, units_values))
  )
)
```

## Cross

The `cross()` transformation defines a target for every combination of grouping variables. 

```{r}
fun_run_values <- rlang::syms(c("good_run", "bad_run", "benchmark_run"))
act_values <- c("relu", "relu", "sigmoid")
expected <- drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act),
    transform = cross(
      fun_run = !!fun_run_values,
      act = !!act_values
    )
  )
)
```

```{r}
dp_table(expected)
```

```{r}
dp_graph(expected)
```

Use `cross()` to create the above plan.

```{r cross, exercise = TRUE, exercise.lines = 17, paged.print = FALSE}
fun_run_values <- rlang::syms(c("good_run", "bad_run", "benchmark_run"))
act_values <- c("relu", "relu", "sigmoid")

drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act),
    transform = map(
      fun_run = !!fun_run_values,
      act = !!act_values
    )
  )
)
```

```{r cross-hint-1}
transform = cross(
  fun_run = !!fun_run_values,
  act = !!act_values
)
```

```{r cross-hint-2}
The next hint has the full solution.
```

```{r cross-hint-3}
fun_run_values <- rlang::syms(c("good_run", "bad_run", "benchmark_run"))
act_values = c("relu", "relu", "sigmoid")
drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act),
    transform = cross(
      fun_run = !!fun_run_values,
      act = !!act_values
    )
  )
)
```

```{r cross-check}
fun_run_values <- rlang::syms(c("good_run", "bad_run", "benchmark_run"))
act_values = c("relu", "relu", "sigmoid")
drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act),
    transform = cross(
      fun_run = !!fun_run_values,
      act = !!act_values
    )
  )
)
```

## Combine

The `combine()` transformation splices together targets generated from previous calls to `map()` and `cross()`. Let's combine all the runs together with `bind_rows()`.

```{r}
fun_run_values <- rlang::syms(c("good_run", "bad_run", "benchmark_run"))
act_values <- c("relu", "relu", "sigmoid")

expected <- drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act),
    transform = cross(
      fun_run = !!fun_run_values,
      act = !!act_values
    )
  ),
  all_runs = target(
    bind_rows(run),
    transform = combine(run)
  )
)
```

```{r}
dp_table(expected)
```

```{r}
dp_graph(expected)
```

Create the above plan using `combine()`.

```{r combine, exercise = TRUE, exercise.lines = 18, paged.print = FALSE}
fun_run_values <- rlang::syms(c("good_run", "bad_run", "benchmark_run"))
act_values <- c("relu", "relu", "sigmoid")

drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act),
    transform = cross(
      fun_run = !!fun_run_values,
      act = !!act_values
    )
  ),
  all_runs = target(
    bind_rows(run),
    transform = ???
  )
)
```

```{r combine-hint-1}
transform = combine(run)
```

```{r combine-hint-2}
The next hint has the complete solution.
```

```{r combine-hint-3}
fun_run_values <- rlang::syms(c("good_run", "bad_run", "benchmark_run"))
act_values <- c("relu", "relu", "sigmoid")

drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act),
    transform = cross(
      fun_run = !!fun_run_values,
      act = !!act_values
    )
  ),
  all_runs = target(
    bind_rows(run),
    transform = combine(run)
  )
)
```

```{r combine-check}
fun_run_values <- rlang::syms(c("good_run", "bad_run", "benchmark_run"))
act_values <- c("relu", "relu", "sigmoid")

drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act),
    transform = cross(
      fun_run = !!fun_run_values,
      act = !!act_values
    )
  ),
  all_runs = target(
    bind_rows(run),
    transform = combine(run)
  )
)
```

## Combine groups

`combine()` has a `.by` argument that lets you combine multiple groups of targets using grouping variables you previously defined (e.g. `combine(runs, .by = act)` or `combine(runs, .by = c(fun_run, act))`).

```{r}
fun_run_values <- rlang::syms(c("good_run", "bad_run", "benchmark_run"))
act_values <- c("relu", "relu", "sigmoid")

expected <- drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act),
    transform = cross(
      fun_run = !!fun_run_values,
      act = !!act_values
    )
  ),
  grouped_runs = target(
    bind_rows(run),
    transform = combine(run, .by = fun_run)
  )
)
```

```{r}
dp_table(expected)
```

```{r}
dp_graph(expected)
```

Create the above plan. Using `combine()` with the `.by` argument, declare a group of runs for each `fun_run` function.

```{r combinegroups, exercise = TRUE, exercise.lines = 18, paged.print = FALSE}
fun_run_values <- rlang::syms(c("good_run", "bad_run", "benchmark_run"))
act_values <- c("relu", "relu", "sigmoid")

drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act),
    transform = cross(
      fun_run = !!fun_run_values,
      act = !!act_values
    )
  ),
  grouped_runs = target(
    bind_rows(run),
    transform = combine(???)
  )
)
```

```{r combinegroups-hint-1}
transform = combine(run, .by = fun_run)
```

```{r combinegroups-hint-2}
The next hint has the complete solution.
```

```{r combinegroups-hint-3}
fun_run_values <- rlang::syms(c("good_run", "bad_run", "benchmark_run"))
act_values <- c("relu", "relu", "sigmoid")

drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act),
    transform = cross(
      fun_run = !!fun_run_values,
      act = !!act_values
    )
  ),
  grouped_runs = target(
    bind_rows(run),
    transform = combine(run, .by = fun_run)
  )
)
```

```{r combinegroups-check}
fun_run_values <- rlang::syms(c("good_run", "bad_run", "benchmark_run"))
act_values <- c("relu", "relu", "sigmoid")

drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act),
    transform = cross(
      fun_run = !!fun_run_values,
      act = !!act_values
    )
  ),
  grouped_runs = target(
    bind_rows(run),
    transform = combine(run, .by = fun_run)
  )
)
```

## Complicated plans

The `map()`, `cross()`, and `combine()` transformations let you chain targets together in intricate ways. Below, let's continue the pipline by mapping over targets we previously defined.

```{r}
fun_run_values <- rlang::syms(c("good_run", "bad_run", "benchmark_run"))
act_values <- c("relu", "relu", "sigmoid")

expected <- drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act),
    transform = cross(
      fun_run = !!fun_run_values,
      act = !!act_values
    )
  ),
  raw_runs = target(
    bind_rows(run),
    transform = combine(run, .by = fun_run)
  ),
  runs = target(
    post_process(raw_runs),
    transform = map(raw_runs, .id = fun_run)
  ),
  runs_plot = target(
    plot_runs(runs, fun_run),
    transform = map(runs, fun_run, .id = fun_run)
  )
)
```

```{r}
dp_table(expected)
```

```{r}
dp_graph(expected)
```

Follow the comments below to create the above plan. Use `.id = fun_run` to shorten the names of the downstream targets.

```{r complicated, exercise = TRUE, exercise.lines = 31, paged.print = FALSE}
fun_run_values <- rlang::syms(c("good_run", "bad_run", "benchmark_run"))
act_values <- c("relu", "relu", "sigmoid")

drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act),
    transform = cross(
      fun_run = !!fun_run_values,
      act = !!act_values
    )
  ),
  raw_runs = target(
    bind_rows(run),
    transform = combine(run, .by = fun_run)
  ),
  # Let's post-process these grouped runs.
  runs = target(
    post_process(raw_runs),
    transform = ??? # Map over the raw runs. Use fun_run for names.
  ),
  # And let's plot them.
  runs_plot = target(
    plot_runs(runs, fun_run),
    transform = ??? # Map over runs and fun_run. Use fun_run for names.
  )
)
```

```{r complicated-hint-1}
transform = map(raw_runs, .id = fun_run)
```

```{r complicated-hint-2}
transform = map(runs, fun_run, .id = fun_run)
```

```{r complicated-hint-3}
runs = target(
    post_process(raw_runs),
    transform = map(raw_runs, .id = fun_run)
  ),
  runs_plot = target(
    plot_runs(runs, fun_run),
    transform = map(runs, fun_run, .id = fun_run)
  )
```

```{r complicated-hint-4}
The next hint has the complete solution.
```

```{r complicated-hint-5}
fun_run_values <- rlang::syms(c("good_run", "bad_run", "benchmark_run"))
act_values <- c("relu", "relu", "sigmoid")

drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act),
    transform = cross(
      fun_run = !!fun_run_values,
      act = !!act_values
    )
  ),
  raw_runs = target(
    bind_rows(run),
    transform = combine(run, .by = fun_run)
  ),
  runs = target(
    post_process(raw_runs),
    transform = map(raw_runs, .id = fun_run)
  ),
  runs_plot = target(
    plot_runs(runs, fun_run),
    transform = map(runs, fun_run, .id = fun_run)
  )
)
```

```{r complicated-check}
fun_run_values <- rlang::syms(c("good_run", "bad_run", "benchmark_run"))
act_values <- c("relu", "relu", "sigmoid")

drake_plan(
  churn_data = split_data(file_in("data/customer_churn.csv")),
  churn_recipe = prepare_recipe(churn_data), 
  run = target(
    fun_run(churn_data, churn_recipe, act1 = act),
    transform = cross(
      fun_run = !!fun_run_values,
      act = !!act_values
    )
  ),
  raw_runs = target(
    bind_rows(run),
    transform = combine(run, .by = fun_run)
  ),
  runs = target(
    post_process(raw_runs),
    transform = map(raw_runs, .id = fun_run)
  ),
  runs_plot = target(
    plot_runs(runs, fun_run),
    transform = map(runs, fun_run, .id = fun_run)
  )
)
```
