---
title: "Set up a drake workflow"
output: html_notebook
---

```{r, include = FALSE}
# Set your working directory to 2-setup/.
# You may have to copy and paste this line into your console:
setwd(file.path(rprojroot::find_rstudio_root_file(), "2-setup"))
source("../config/options.R")
```

After working through `1-churn.Rmd`, we have the building blocks of our data analysis project. Now, let's put the pieces together in a `drake`-powered reproducible workflow.

# Dependencies

To set up a [`drake`](http://github.com/ropensci/drake) workflow for the customer churn case study, we first load our packages and functions into the current R session.

```{r message = FALSE}
source("R/packages.R")  # Load the packages.
source("R/functions.R") # Define our custom functions.
```

 Open up `packages.R` and `functions.R` scripts and take a look at how they are organized.

# Plan

Now, it is time to plan the actual workflow. If you were to write an R script, this is what it would look like.

```{r, eval = FALSE}
# Get the data.
data = read_csv(
  file_in("../data/customer_churn.csv"),
  col_types = cols()
) %>%
  initial_split(prop = 0.3)

# Create the recipe.
rec <- prepare_recipe(data)

# Train the model.
model <- train_model(data, rec)

# Compare to testing data.
conf <- confusion_matrix(data, rec, model)

# Compute performance metrics.
metrics <- compare_models(conf)
```

But for [`drake`](http://github.com/ropensci/drake)-powered automation and reproducibility, we use a special data frame called a [`drake` plan](https://ropenscilabs.github.io/drake-manual/plans.html). Fill out the [`drake`](http://github.com/ropensci/drake) plan below. The "targets" (`data`, `rec`, etc.) can be in any order.

```{r}
plan <- drake_plan(
  rec = , # Create the recipe.

  model = , # Train the model.

  conf = , # Compare to testing data.

  metrics = , # Compute performance metrics.
    
  data = read_csv( # Get the data. Filled in for you already.
    file_in("../data/customer_churn.csv"),
    col_types = cols()
  ) %>%
    initial_split(prop = 0.3),
)
```

The plan is just a fancy data frame. Each command is a step in the workflow, and each target will store the return value of a command. 

```{r, paged.print = FALSE, warning = FALSE}
plan
```

# Check the plan.

Did you write the plan correctly? Let's find out with a dependency graph. The graph is interactive. Zoom and drag for a better view.

```{r, message = FALSE}
config <- drake_config(plan)
vis_drake_graph(config, hover = TRUE)
```

If you wrote the plan properly, your graph should look something like this.

```{r}
library(visNetwork)
readRDS("img/graph.rds")
```

# Do the work.

Call [`make()`](https://ropensci.github.io/drake/reference/make.html) to actually run the workflow. `make()` builds the targets from left to right in the dependency graph. The output is stored in a hidden `.drake/` cache.

```{r}
make(plan)
```

Try `make()` again. What happens?

```{r}
make(plan)
```

The graph displays the status of targets.

```{r}
vis_drake_graph(config)
```

Let's load some targets from on-disk storage.

```{r}
loadd(data)
training(data) %>%
  select(Churn, customerID, TotalCharges) %>%
  head(n = 6)
```

```{r}
readd(metrics) # see also loadd()
```

# Start over

If you ever want to start over, use `clean()` to "invalidate" the targets (force them to be out of date).

```{r}
clean()
```

The next `make()` runs everything from scratch.

```{r}
make(plan)
```

# History

`drake` version 7.5.0 and above tracks history and provenance. You can see which models you ran, when you ran them, how long they took, and which settings you tried.

```{r churnhistory}
history <- drake_history()
history
```

And as long as you did not run `clean(garbage_collection = TRUE)`, you can get the old data back. Let's find the oldest run of the model.

```{r churnhistory2}
hash <- history %>%
  filter(target == "model") %>%
  pull(hash) %>%
  head(n = 1)
cache <- drake_cache()
cache$get_value(hash) %>%
  unserialize_model()
```
