---
title: "Practice a drake workflow."
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(praise)
options(
  drake_make_menu = FALSE,
  drake_clean_menu = FALSE,
  warnPartialMatchArgs = FALSE,
  crayon.enabled = FALSE,
  readr.show_progress = FALSE
)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE
)
laud <- function() {
  praise("${Exclamation}! ${Adverb} ${adjective} answer.")
}
```

## Instructions

1. Download the HTML notebooks and supporting files with [`learndrake::save_notebooks()`](https://github.com/wlandau/learndrake).
2. Open [3-flow/3-flow.Rmd](https://github.com/wlandau/learndrake/blob/master/inst/notebooks/3-flow/3-flow.Rmd) in a fresh R session.
3. Make sure your working directory is the same as `3-flow.Rmd` (use the setup chunk at the top).
4. Step through these exercises in order. Unless otherwise indicated, run the code chunks in your R console. Check the answers as you go along.
5. If something breaks along the way, you restart your R session and get a fresh copy of the notebooks and supporting files ([`learndrake::save_notebooks()`](https://github.com/wlandau/learndrake)).

```{r q0}
question(
  "Okay?",
  correct = laud(),
  incorrect = "Let's talk.",
  allow_retry = TRUE,
  random_answer_order = TRUE,
  answer("Yes", correct = TRUE),
  answer("No"),
  answer("My computations run too fast to ever need drake."),
  answer("I have waited my whole life for this question.")
)
```

## Exercise 1

In your working directory (should be `3-flow`) there should be an `R/` folder with 3 scripts.

```{r, echo = TRUE}
list.files("R")
```

Run them to get your R session ready for [`drake`](https://ropensci.github.io/drake).

```{r, message = FALSE, echo = TRUE}
source("R/packages.R")
source("R/functions.R")
source("R/plan.R")
```

```{r q1}
question(
  "Okay?",
  correct = laud(),
  incorrect = "Let's talk.",
  allow_retry = TRUE,
  random_answer_order = FALSE,
  answer("Yes", correct = TRUE),
  answer("No"),
  answer("Why?"),
  answer("No seriously, why? I need to understand this before we move on.")
)
```

## Exercise 2

You now have a [plan](https://ropenscilabs.github.io/drake-manual/plans.html).

```{r paged.print = FALSE, echo = TRUE}
print(plan)
```

Did creating the [plan](https://ropenscilabs.github.io/drake-manual/plans.html) actually run the workflow? Hint: [`cached()`](https://ropensci.github.io/drake/reference/cached.html).

```r
cached()
```

```{r q2}
question(
  "Answer",
  correct = laud(),
  incorrect = paste(
    "make() is the function that actually runs the workflow.",
    "Creating the plan with drake_plan() does not build any targets."
  ),
  allow_retry = TRUE,
  random_answer_order = TRUE,
  answer("Yes"),
  answer("No", correct = TRUE)
)
```

## Exercise 3

Let's look at the row order of the [plan](https://ropenscilabs.github.io/drake-manual/plans.html).

```{r paged.print = FALSE, echo = TRUE}
print(plan)
```

When you call [`make()`](https://ropensci.github.io/drake/reference/make.html) in your R console, which target runs *first*? Why?

```r
make(plan)
```

```{r q3}
question(
  "Answer",
  correct = laud(),
  incorrect = "Run `drake::clean()` and try again.",
  allow_retry = TRUE,
  random_answer_order = TRUE,
  answer("`metrics`, because it is in the first row."),
  answer("`data`, because the other targets depend on it.", correct = TRUE),
  answer("`rec`, because the other targets depend on it.")
)
```

## Exercise 4

When you called [`make()`](https://ropensci.github.io/drake/reference/make.html) in the previous exercise, which target ran *last*? Why?

```{r q4}
question(
  "Answer",
  correct = laud(),
  incorrect = "Run `drake::clean()` and try again.",
  allow_retry = TRUE,
  random_answer_order = TRUE,
  answer("`metrics`, because it depends on the results all the other targets.", correct = TRUE),
  answer("`data`, because it is listed last."),
  answer("`rec`, because it is listed second.")
)
```

## Exercise 5

Load `metrics` from the hidden `.drake/` cache and print it out. What do you see?

```r
loadd(metrics)
print(metrics)
```

```{r q5}
question(
  "Answer",
  correct = laud(),
  incorrect = "Let's talk.",
  allow_retry = TRUE,
  random_answer_order = TRUE,
  answer("A confusion matrix."),
  answer("A confusing matrix."),
  answer("A plot of our model's performance metrics", correct = TRUE),
  answer("A generic method from the `yardstick` package.")
)
```

## Exercise 6

Run [`make()`](https://ropensci.github.io/drake/reference/make.html) again. What happens?

```r
make(plan)
```

```{r q6}
question(
  "Answer",
  correct = laud(),
  incorrect = "Let's talk.",
  allow_retry = TRUE,
  random_answer_order = TRUE,
  answer("`drake` builds nothing because all the targets are already up to date.", correct = TRUE),
  answer("`drake` refits the model."),
  answer("All my targets rebuild."),
  answer("What is a target? Either that was not explained or I forgot.")
)
```


## Exercise 7

Restart your R session and run the full workflow from beginning to end. Which targets rebuild, if any?

```r
# Restart R. (Look under "Session" in RStudio's top menu bar.)
source("R/packages.R")
source("R/functions.R")
source("R/plan.R")
make(plan)
```

```{r q7}
question(
  "Answer",
  correct = laud(),
  incorrect = "Let's talk.",
  allow_retry = TRUE,
  random_answer_order = TRUE,
  answer("All of them."),
  answer("`drake` fits the model all over again."),
  answer("I get a confusing error message."),
  answer("None. The targets are all in storage (a hidden `.drake/` folder) and still up to date.", correct = TRUE)
)
```

## Exercise 8

Open `R/functions.R` for editing. At the bottom of `compare_models()`, change `theme_gray(16)` to `theme_gray(24)`. Save the file but **do not run it or `source()` it into your R session**.

```r
compare_models <- function(...) {
  # Rest of the function body... 
  theme_gray(24) # Change 16 to 24 here.
}
```

Run [`make()`](https://ropensci.github.io/drake/reference/make.html) only (*without* `source("R/functions.R")`).

```r
# Edit and save R/functions.R.
make(plan)
```

What happens?

```{r q8}
question(
  "Answer",
  correct = laud(),
  incorrect = "Let's talk.",
  allow_retry = TRUE,
  random_answer_order = TRUE,
  answer("All my targets rebuild."),
  answer("The `metrics` target rebuilds because I changed `compare_models()` in `R/functions.R`."),
  answer("Nothing. My R session still has the old version of `compare_models()` in memory.", correct = TRUE)
)
```

## Exercise 9

Now, run `R/functions.R` and then run [`make()`](https://ropensci.github.io/drake/reference/make.html) again.

```r
# Edit and save R/functions.R.
source("R/functions.R")
make(plan)
```

Which targets rebuild, if any?

```{r q9}
question(
  "Answer",
  correct = laud(),
  incorrect = "Let's talk.",
  allow_retry = TRUE,
  random_answer_order = TRUE,
  answer("None, because `metrics` updated last time."),
  answer("`metrics`, because my R session now has the new version of `compare_models()`.", correct = TRUE),
  answer("All of them.")
)
```

## Exercise 10

In `R/plan.R`, choose `"sigmoid"` for the activation function of the first layer of our deep neural network.

```r
# Make this change in R/plan.R.
# Do not run in the console.
plan <- drake_plan(
  # ...
  model = train_model(data, rec, act1 = "sigmoid") # edit here
  # ...
)
```

Save `R/plan.R`, source it, and run [`make()`](https://ropensci.github.io/drake/reference/make.html) again. Which targets rebuild, if any?

```r
# Edit and save R/plan.R.
source("R/plan.R")
make(plan)
```

```{r q10}
question(
  "Answer",
  correct = laud(),
  incorrect = "Let's talk.",
  allow_retry = TRUE,
  random_answer_order = TRUE,
  answer("`model` only."),
  answer("`model`, `conf`, and `metrics` (because `conf` and `metrics` depend on `model`).", correct = TRUE),
  answer("None.")
)
```

## Exercise 11

In `R/functions.R`, add a comment inside the body of `confusion_matrix()`. Leave the rest of the function alone.

```r
confusion_matrix <- function(data, rec, serialized_model) {
  # Add a comment anywhere in the body.
  model <- unserialize_model(serialized_model) # Leave the rest alone.
  # ...
}
```

Save and run `R/functions.R` and then run [`make()`](https://ropensci.github.io/drake/reference/make.html).

```r
# Edit and save R/functions.R
source("R/functions.R")
make(plan)
```

Which targets rebuild, if any?

```{r q11}
question(
  "Answer",
  correct = laud(),
  incorrect = "Let's talk.",
  allow_retry = TRUE,
  random_answer_order = TRUE,
  answer("`conf`, because I changed `confusion_matrix()`."),
  answer("`conf` and `metrics`, because I changed `confusion_matrix()`."),
  answer("None, because `drake` ignores changes to comments and whitespace.", correct = TRUE),
  answer("All of them, because the code changed.")
)
```

## Exercise 12

Which targets are downstream of `conf`? Find out with  [`vis_drake_graph()`](https://ropensci.github.io/drake/reference/vis_drake_graph.html).

```r
config <- drake_config(plan)
vis_drake_graph(config, hover = TRUE)
```

```{r q12}
question(
  "Answer",
  correct = laud(),
  incorrect = "Let's talk.",
  allow_retry = TRUE,
  random_answer_order = TRUE,
  answer("`metrics`", correct = TRUE),
  answer("`metrics` and `conf`"),
  answer("`model`"),
  answer("`data` and `model`"),
  answer("All of them.")
)
```

## Exercise 13

In `R/functions.R`, add a print statement in the body of `confusion_matrix()`. Leave the rest of the function alone.

```r
confusion_matrix <- function(data, rec, serialized_model) {
  print("Building a confusion matrix.") # Add something like this.
  model <- unserialize_model(serialized_model)
  # ...
}
```

Save and run `R/functions.R` and then run [`make()`](https://ropensci.github.io/drake/reference/make.html).

```r
# Edit and save R/functions.R.
source("R/functions.R")
make(plan)
```

Which targets rebuild, if any?

```{r q13}
question(
  "Answer",
  correct = laud(),
  incorrect = "Let's talk.",
  allow_retry = TRUE,
  random_answer_order = TRUE,
  answer("`metrics` and `conf`, because we changed `confusion_matrix()` and `metrics` is downstream."),
  answer("`conf` only. We changed `confusion_matrix()` but still get the same return value. Thus, `metrics` is still up to date.", correct = TRUE),
  answer("Nothing, because `drake` can predict `confusion_matrix()` would return the same value."),
  answer("Everything.")
)
```

## Exercise 14

Delete the last record of `../data/customer_churn.csv` and run [`make()`](https://ropensci.github.io/drake/reference/make.html) again. Which targets  rebuild? Why?

```r
# Open ../data/customer_churn.csv in the RStudio IDE ("View File").
# Delete the last record.
# Save the file.
make(plan)
```

```{r q14}
question(
  "Answer",
  correct = laud(),
  incorrect = "Let's talk.",
  allow_retry = TRUE,
  random_answer_order = TRUE,
  answer("Nothing, because `drake` only tracks functions and commands."),
  answer("Everything, because all our targets are downstream of the data file.", correct = TRUE),
  answer("Everything, because `drake` always indiscriminately runs everything.")
)
```
